\begin{thebibliography}{30}

\bibitem{Nvidia-architecture} NVIDIA, \emph{The Benefits of Using GPUs}, CUDA documentation \url{https://docs.nvidia.com/cuda/cuda-c-programming-guide/index.html#introduction}

\bibitem{Nvidia-story} NVIDIA, \emph{Cronologia di NVIDIA, una storia di innovazione}. \url{https://www.nvidia.com/it-it/about-nvidia/corporate-timeline/}

\bibitem{leading-dimension} IBM, \emph{How Leading Dimension Is Used for Matrices}, IBM documentation \url{https://www.ibm.com/docs/en/essl/6.3?topic=matrices-how-leading-dimension-is-used}

\bibitem{prof-paper} Conte, D. et al. (2022). First Experiences on Parallelizing Peer Methods for Numerical Solution of a Vegetation Model. In: Gervasi, O., Murgante, B., Hendrix, E.M.T., Taniar, D., Apduhan, B.O. (eds) Computational Science and Its Applications – ICCSA 2022. ICCSA 2022. Lecture Notes in Computer Science, vol 13376. Springer, Cham. \url{https://doi.org/10.1007/978-3-031-10450-3_33}

\bibitem{bib:self-organization} Eigentler, L., Sherratt, J.A. Metastability as a Coexistence Mechanism in a Model for Dryland Vegetation Patterns. Bull Math Biol 81, 2290–2322 (2019). https://doi.org/10.1007/s11538-019-00606-z

\bibitem{two-step-peer-methods} Weiner, R., Biermann, K., Schmitt, B., Podhaisky, H.: Explicit two-step peer methods.
Comput. Math. Appl. 55(4), 609–619 (2008)

\bibitem{runge-kutta} Butcher, J.C.: Implicit Runge-Kutta processes. Math. Comp. \textbf{18}, 50–64 (1964)

\bibitem{ODEs} Butcher, J.C.: Numerical Methods for Ordinary Differential Equations, 2nd edn. Wiley, Chichester (2008)

\bibitem{method-of-line} Samir Hamdi et al. (2007) Method of lines. Scholarpedia, 2(7):2859. \url{http://www.scholarpedia.org/article/Method_of_lines}

\bibitem{implicit-runge-kutta} Butcher, J.C.: Implicit Runge-Kutta processes. Math. Comp. 18, 50–64 (1964)

\bibitem{implicit-runge-kutta-2} Butcher, J.C.: Numerical Methods for Ordinary Differential Equations, 2nd edn.
Wiley, Chichester (2008)

\bibitem{general-linear-methods} Butcher, J.C.: General linear methods. Acta Numer. 15, 157–256 (2006)

\bibitem{runge-kutta-convergence} Sanz-Serna, J.M., Verwer, J.G. and Hundsdorfer, W.H. Convergence and order reduction of Runge Kutta schemes applied to evolutionary problems in partial differential equations. Numer. Math. 50, 405–418 (1986). \url{https://doi.org/10.1007/BF01396661}

\bibitem{cuda-environment} \url{https://developer.nvidia.com/cuda-zone}

\bibitem{peer-methods-1} Conte, D., Mohammadi, F., Moradi, L., Paternoster, B.: Exponentially fitted twostep
peer methods for oscillatory problems. Comput. Appl. Math. 39(3), 1–19
(2020). \url{https://doi.org/10.1007/s40314-020-01202-x}

\bibitem{peer-methods-2} Conte, D., Pagano, G., Paternoster, B.: Jacobian-dependent two-stage peer method
for ordinary differential equations. In: Gervasi, O., et al. (eds.) ICCSA 2021, Part I.
LNCS, vol. 12949, pp. 309–324. Springer, Cham (2021). \url{https://doi.org/10.1007/978-3-030-86653-2_23}

\bibitem{peer-methods-3} Conte, D., Pagano, G., Paternoster, B.: Two-step peer methods with equation dependent
coefficients. Comput. Appl. Math. 41(4), 140 (2022)

\bibitem{peer-methods-4} Schmitt, B.A., Weiner, R., Jebens, S.: Parameter optimization for explicit parallel
peer two-step methods. Appl. Numer. Math. 59(3–4), 769–782 (2009)
394 D. Conte et al.

\bibitem{peer-methods-5} Schmitt, B.A., Weiner, R., Podhaisky, H.: Multi-implicit peer two-step W-methods
for parallel time integration. BIT Numer. Math. 45(1), 197–217 (2005). \url{https://doi.org/10.1007/s10543-005-2635-y}

\bibitem{peer-methods-6} Schmitt, B.A., Weiner, R., Erdmann, K.: Implicit parallel peer methods for stiff
initial value problems. Appl. Numer. Math. 53(2–4), 457–470 (2005)

\bibitem{peer-methods-7} Weiner, R., Schmitt, B.A., Podhaisky, H.: Parallel “Peer” two-stepW-methods and
their application to MOL-systems. Appl. Numer. Math., 48(3–4), 425–439 (2004)
18. Schmitt, B.A.,Weiner, R.: Parallel two-stepW-methods with peer variables. SIAM
J. Numer. Anal. 42(1), 265–282 (2004)

\bibitem{peer-methods-8} Jebens, S., Weiner, R., Podhaisky, H., Schmitt, B.: Explicit multi-step peer methods
for special second-order differential equations. Appl. Math. Comput. 202(2),
803–813 (2008)

\bibitem{peer-methods-9} Klinge, M., Weiner, R., Podhaisky, H.: Optimally zero stable explicit peer methods
with variable nodes. BIT Numer. Math. 58(2), 331–345 (2017). https://doi.org/
10.1007/s10543-017-0691-8

\bibitem{peer-methods-10} Rosenbrock, H.H.: Some general implicit processes for the numerical solution of differential equations. Comput. J. 5(4), 329–330 (1963)

\end{thebibliography}
